Integrated nested Laplace approximations for extended latent Gaussian models with application to the Naomi HIV model

### 2023-01-20 src/docs_paper/paper.Rmd
Add to acknowledgements section

AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1).

>>>>

AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1).
AH and JWE were supported by the Bill and Melinda Gates Foundation (OPP1190661, OPP1164897).
AS was supported by...
SRF was supported by the EPSRC (EP/V002910/2).
JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664).
This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth \& Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.
